Data analysis to prioritise new cycleways in response to COVID-19

### 2020-06-03 article.Rmd
Add references

---
title: "Methods to prioritise pop-up active transport infrastructure"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Malcolm Morgan, Joey Talbot, Martin-Lucas-Smith"
# output: bookdown::github_document2
# output: bookdown::html_document2
# output:
#   bookdown::pdf_document2:
#     keep_tex: true
# bibliography: references.bib
bibliography: ref.bib
---

@@

```{r, echo=FALSE, eval=FALSE}
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "ref.bib")
wordcountaddin::word_count("article.Rmd")
knitr::purl("article.Rmd")
file.copy("article.R", "code/article-methods-1.R")
pagedown::chrome_print("article.html")
browseURL("article.pdf")
zf = list.files(pattern = "tex|png", full.names = TRUE)
zfl = list.files("article_files/figure-latex/", full.names = TRUE)
fz = c(zf, zfl)
msgf = paste(fz, collapse = " ")
msgf = gsub(pattern = "\\./", replacement = "", msgf)
msg = paste("tar -cvf article.tar ", msgf)
system(msg)
```

>>>>

---
title: "Methods to prioritise pop-up active transport infrastructure"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Malcolm Morgan, Joey Talbot, Martin-Lucas-Smith"
# output: bookdown::github_document2
# output: bookdown::html_document2
# output:
#   bookdown::pdf_document2:
#     keep_tex: true
# bibliography: references.bib
bibliography: refs.bib
---

@@

```{r, echo=FALSE, eval=FALSE}
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "refs.bib")
wordcountaddin::word_count("article.Rmd")
knitr::purl("article.Rmd")
file.copy("article.R", "code/article-methods-1.R")
pagedown::chrome_print("article.html")
browseURL("article.pdf")
zf = list.files(pattern = "tex|png", full.names = TRUE)
zfl = list.files("article_files/figure-latex/", full.names = TRUE)
fz = c(zf, zfl)
msgf = paste(fz, collapse = " ")
msgf = gsub(pattern = "\\./", replacement = "", msgf)
msg = paste("tar -cvf article.tar ", msgf)
system(msg)
```

### 2020-06-03 code/index.Rmd
Add references

---
title: "Rapid cycleway prioritisation tool"
author: "Dr Robin Lovelace & Dr Joey Talbot, Institute for Transport Studies, University of Leeds"
output: 
  html_document: 
    toc: yes
---

@@

@@

This tool helps identify road sections for road space reallocation and other interventions to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
The evidence may be used to support a range of temporary, experimental and permanent treatments that will enable shift to walking and cycling in the coming weeks and months, to help overcome capacity constraints on public transport modes and prevent gridlock as the lockdown eases.

Maps are available for regions covering the whole of England.

The focus is on roads that have 'spare space' (defined as those with a spare lane or that have an estimated width of above 10 m) and high cycling potential.
The 10 m width is an indicator of road conditions and larger widths, of 15+ m, may be required for road space reallocation without other changes such as making roads one way for motor traffic or removing central markings as described in a paper by Stella Shackel and John Parkin ([2014](https://doi.org/10.1016/j.aap.2014.08.015)).
Which roads to prioritise and the most effective interventions will also depend on factors such as on street parking levels not present in the analysis.

@@

## 1. Cohesive network

The layer takes no account spare space and is designed to support consideratioin of alternative options, e.g. one way streets, where there may be insufficient space for road space reallocation without changing the navigable network for motor traffic.
The cohesive network layer was created based on evidence that cohesive cycle networks, that are continuous and do not 'give up' at awkward junctions, are a key component of plans to get people cycling.

## 2. Existing cycleways

This layer shows existing cycleways. This may be helpful to view in connection with the other layers, because it can reveal where gaps in the existing cycle network could be filled by new infrastructure. This layer does not include some on-road cycle lanes or cycleways less than 500m in length, but these can be viewed in one of the basemap options (see below for more information about the basemaps).
The definition of 'cycleway' includes shared use paths but excludes cycle lanes painted on roads in this layer.

## 3. Top ranked new cycleways

@@

>>>>

---
title: "Rapid cycleway prioritisation tool"
author: "Dr Robin Lovelace & Dr Joey Talbot, Institute for Transport Studies, University of Leeds"
output: 
  html_document: 
    toc: yes
bibliography: 
  # - index.bib
  - ../refs.bib
---

```{r, eval=FALSE, echo=FALSE}
citr::tidy_bib_file("~/uaf/allrefs.bib", rmd_file = "code/index.Rmd", file = "code/index.bib")
```

@@

```{r bibs, engine='bash', eval=FALSE}
bibtool
ls *.bib
bibtool refs.bib report-refs.bib code/index.bib > refs.bib
```

@@

The rapid cycleway prioritisation tool helps identify road sections for road space reallocation and other interventions to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
In the context of COVID-19, big decisions need to be made **rapidly**.

The rapid cycleway prioritisation tool aims to help produce evidence-based answers the question: **where to reallocate road space on arterial routes away from motor traffic and towards active transport?**
The evidence can be used to support a range of temporary, experimental and permanent treatments that will enable shift to walking and cycling in the coming weeks and months.
The focus of the tool is road space reallocation on strategic corridors, a key way in which transport systems can be transformed to overcome capacity constraints on public transport modes and prevent gridlock as the lockdown eases.

Maps are currently available for regions covering the whole of England.

The focus is on roads that have 'spare space' (defined as those with a spare lane or that have an estimated width of above 10 m) and high cycling potential based on the [Propensity to Cycle Tool](https://www.pct.bike/) [@lovelace_propensity_2017].
The 10 m width is an indicator of road conditions and larger widths, of 15+ m, may be required for road space reallocation without other changes such as making roads one way for motor traffic or removing [central markings](https://doi.org/10.1016/j.aap.2014.08.015) [@shackel_influence_2014].
Which roads to prioritise and the most effective interventions will also depend on factors such as on street parking levels not present in the analysis.

@@

## 1. Existing cycleways

On the basis that plans should build on and extend existing provision, this layer shows existing cycleways.
This may be helpful to view in connection with the other layers, because it can reveal where gaps in the existing cycle network could be filled by new infrastructure.
This layer does not include some on-road cycle lanes or cycleways less than 500m in length, but these can be viewed in one of the basemap options (see below for more information about the basemaps).
The definition of 'cycleway' includes shared use paths but excludes cycle lanes painted on roads in this layer.

## 2. Top ranked new cycleways

@@

## 3. Cohesive network

The layer takes no account spare space and is designed to support consideration of alternative options, e.g. one way streets, where there may be insufficient space for road space reallocation without changing the navigable network for motor traffic.
The cohesive network layer was created based on evidence that cohesive cycle networks, that are continuous and do not 'give up' at awkward junctions, are a key component of plans to get people cycling.

### 2020-06-03 report.Rmd
Add references

---
title: "Data analysis to prioritise new cycleways in response to COVID-19"
author: Dr Robin Lovelace & Dr Joey Talbot, Institute for Transport Studies, University of Leeds
output: bookdown::pdf_document2
bibliography: report-refs.bib
---

```{r, eval=FALSE, echo=FALSE}
citr::tidy_bib_file("~/uaf/allrefs.bib", rmd_file = "report.Rmd", file = "report-refs.bib")
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "ref.bib")
browseURL("report.pdf")
```

>>>>

---
title: "Data analysis to prioritise new cycleways in response to COVID-19"
author: Dr Robin Lovelace & Dr Joey Talbot, Institute for Transport Studies, University of Leeds
output: bookdown::pdf_document2
bibliography: refs.bib
---

```{r, eval=FALSE, echo=FALSE}
citr::tidy_bib_file("~/uaf/allrefs.bib", rmd_file = "report.Rmd", file = "refs.bib")
citr::tidy_bib_file("~/uaf/allrefs.bib", rmd_file = "code/index.Rmd", file = "refs.bib")
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "refs.bib")
browseURL("report.pdf")
```
